---
title: "TTE Module Integration"
author: "Stefan Eng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TTE Module Integration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE,
  warning = FALSE
)
```

## Introduction

The TTE (time-to-event) modules are [`{tidymodules}`](https://opensource.nibr.com/tidymodules), which are R6 classes.
The TTE collection of modules features three main modules:

  - [TTE](#TTE)
  - [TTEMapping](#TTEMapping)
  - [SubgroupManager](#SubgroupManager)

If you are integrating this into a project you generally will not need the Mapping module as you will already know which variables you will be including in your models.
The mapping module is useful if you want to load multiple data sets that have inconsistent naming schemes, such as ADaM and NOVDD.

Before including these in your application it is good to be familiar with standard Shiny modules.
A good introduction is available here: https://shiny.rstudio.com/articles/modules.html

## TTE {#TTE}
The TTE Module features include:

  - Kaplan Meier Survival Plot
  - Event summary tables
  - Cox proportional hazard model
    - Forest plot
    - Hazard ratio estimates and confidence intervals
    

We can run this example with the following code:
```{r}
subpat::subpatExamples("06_tte_simple")
```

There are a few main parts that are different from regular Shiny modules.
The first step is that we need to _initialize_ the module with

```{r, eval = T}
library(subpat)
tteModule <- TTE$new()
```

We can optionally give our module an id by passing `id = my_id` as a parameter to `new`.
The module will dynamically create an id if we do not specify one.
We can see what the module looks like by printing it

```{r, eval = T}
tteModule
```

Here we can see the namespace that was generated, the input ports and the output ports.
You can think of the input ports as the parameters to a function.
The output ports are the values that are returned from the module.
Here we can see that there is nothing being returned, since this module just displays data.
We can refer to the input or output ports by name or by number.
In the TTE modules, options is always the last input port.

The next step is to call our module somewhere in the server function:
```{r, eval = F}
tteModule$callModule()
```

This is identical to using Shiny's `callModule` function except that we do not have to keep track of the id of the module.

The next step is to pass data and options into our module.
There are two ways to pass data into a TidyModule: through pipes, and explictly.
The elegant way to do this with tidymodules (and why is is named _tidy_ modules), is through pipes.
The basic formula to pass data into a module is `my_reactive %>j% MyModule`.
This will pass the `my_reactive` reactive value into the jth input port of `MyModule`.
Let's try this with the TTE module:

```{r, eval = F}

# Create a reactive of the NCCTG Lung Cancer Data Set from the survival package
data_reactive <- reactive({
  survival::lung
})

# Pass the data into the TTE module
# This needs to be in a server function and reactive context:
# E.g: isolate, observe, observeEvent, etc.
isolate({
  data_reactive %>1% tteModule
})
```

Now we have the data passed into the module. Currently the module will not do much since it expects the `mapping` parameter to be provided.
The mapping is a reactive list of values that map the variables from your data set into the correct parameter.
The parameters are:

  - `time`
  - `event`
  - `treatment`
  - `strata`
  - `parameter`
  - `parameter_value`
  - `population`
  - `aval_conv`
  
```{r, eval = F}
# Set the variable names to use in the model
# See the information about the variables with
# help(lung)
mapping <- reactive({
  list(
    time = 'time',
    event = 'status',
    treatment = 'sex',
    # Conversion factor: makes the time number of months.
    aval_conv = 30.34
  )
})

# Pass the mapping into the second input port
isolate({
  mapping %>2% tteModule
})
```

We can also pass options into the module in a similar way.
Options expects a reactive function.
There are two options that we can pass into the module:

  -  `makePlotly` Should the graph be interactive via plotly? Note, enabling this is experimental and the survival plots do not always look great. Default: `FALSE`
  - `conftype` The confidence interval type. Choice between: "none", "plain", "log", or "log-log". Default: "log-log"
  
```{r, eval = F}
options <- reactive(list(
    makePlotly = FALSE,
    conftype = "log-log"
  ))

isolate({
  options %>4% tteModule
})
```

That's all you need to include the TTE module in your application. The full application is available below:

```{r, code = readLines(system.file("shiny-examples/06_tte_simple/app.R", package = "subpat"))}
```

## SubgroupManager {#SubgroupManager}

The subgroup module is currently a prototype, which is not as full featured as I would like.
If you would like to test it out anyway, the code is easy to integrate into your own application.

```{r, code = readLines(system.file("shiny-examples/08_subgroup/app.R", package = "subpat"))}
```

